<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2015-04-28 background/background1.Rmd
WIP: regular update
ENH:  Adding circularity section.
ENH:  More slides for compeittion.

<div align="center"><img width="1800" src="./figures/bant2.png" frameborder="0"></img></div>

BBA & NT

@@

* (maybe he should have used ANTs?)

@@

## ANTs Lineage

@@

@@

## ANTs: Beyond Registration

@@

```

![](figures/handsaw.jpg)

simple and nearly self-explanatory

>>>>

<div align="center"><img width="1800" src="./figures/brian_and_nick.png" frameborder="0"></img></div>

BBA & NJT

@@

* (maybe he should have used *ANTs*?)

## Image mapping & biology: 1917

![](./figures/dthompson.png)

D'Arcy Thompson

@@

## *ANTs* Lineage

@@

## Diffeomorphisms: image parameterization in a metric space

![](./figures/shape_appearance.png)

@@

## *ANTs*: Beyond Registration

@@

### 2015-04-28 competitions/competitions.Rmd
ENH:  More slides for compeittion.

##

![](./evaluation/figures/evalhistory.png)

@@

_"Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with ANTsR"_

>>>>

## <span style="color:green;">Competitions</span>

* [Klein 2009](http://www.ncbi.nlm.nih.gov/pubmed/19195496)
* [EMPIRE 2010](http://empire10.isi.uu.nl)
* [Multi-Atlas Label Challenge 2012](https://masi.vuse.vanderbilt.edu/workshop2012/index.php/Main_Page)
* [SATA Challenge 2013](https://masi.vuse.vanderbilt.edu/workshop2013/index.php/MICCAI_2013_SATA_Challenge_and_Workshop:Current_events)
* [BRATS 2013](http://martinos.org/qtim/miccai2013/)
* [STACOM 2014 MoCo Challenge](http://www.cardiacatlas.org/web/stacom2014/moco-introduction)

<!--- ![](./evaluation/figures/evalhistory.png) -->

## <span style="color:green;">Klein 2009</span> <small>brain image registration</small>

![](./competitions/figures/nihms-130679-f0001.jpg)

* 14 algorithms
* publicly available data
* unbiased evaluation

## <span style="color:green;">Klein 2009</span> <small>results</small>

![](./competitions/figures/KleinResults2009.png)

_"One of the most significant findings of this study is that the relative performances of
the registration methods under comparison appear to be little affected by the choice of
subject population, labeling protocol, and type of overlap measure....  ART, SyN, IRTK, and
SPM's DARTEL Toolbox gave the best results according to overlap and distance measures,
with ART and SyN delivering the most consistently high accuracy across subjects and label sets."_

## <span style="color:green;">EMPIRE 2010</span> <small>lung image registration</small>

## <span style="color:green;">Multi-Atlas Label Challenge 2012</span> <small>atlas label fusion</small>

## <span style="color:green;">SATA Challenge 2012</span> <small>multi-modal/multi application label fusion</small>

@@

_Optimal symmetric multimodal templates and concatenated random forests for
supervised brain tumor segmentation (simplified) with ANTsR_
